Spike-and-Slab Generalized Additive Models and Fast Algorithms for High-Dimensional Data

### 2021-06-29 Manuscript/01-Intro.Rmd
* Revise the notation section of the Method * Correct typo and grammar in intro

To address these challenges, we propose a novel Bayesian hierarchical generalized additive model (BHAM) for high dimensional data analysis. Specifically, we impose a new bi-part spike-and-slab spline prior on the smooth functions to perform bilevel selection, where the linear and nonlinear spaces of smooth functions can be selected separately. The prior setup encourages a flexible solution, rending one of three possibilities: no effect, only linear effect, or nonlinear effect of a predictor. Additionally, two fast computing optimization based algorithms are developed for high and ultra-high dimension settings respectively. Meanwhile, to avoid the over-penalization of the basis function coefficients, smoothness penalties are incorporated in the model via re-parameterization. Smoothness penalties are commonly implemented in GAMs through smoothing and penalized regression splines. They are quadratic norm of the coefficients, and allow locally adaptive penalties on each smoothing function. For the most common case of cubic splines, the smoothness penalty conditioning on a smoothness penalty parameter $\lambda_j$ is a function of the integration of second derivative of the spline function, expressed mathematically as
\begin{equation}\label{eq:smoothpen}
  \text{pen}\left[f_j(x)\right] = \lambda_j \int f^{"}_j(x)dx = \lambda_j \bs \beta_j^T \bs S_j \bs \beta_j ,
\end{equation}
where $\bs S_j$ is a known penalty matrix, and $\bs \beta_j$ are the basis function coefficients. Smoothness penalties are also previously used in the spike-and-slab GAM [@Scheipl2012] and the sparsity-smoothness penalty [@Meier2009]. Moreover, incorporating the smoothness penalty allows the separation of the linear space of the smooth function, also know as the null space, from the nonlinear space. @Marra2011 introduced a re-parameterization of the basis function matrix based on the decomposition of the smoothness penalty matrix $\bs S$. The re-parameterization allows different penalties imposed on the null and nonlinear spaces separately, and further allows the sparsity in linear space and smoothness in nonlinear effect interpolation. [TODO: a sentence that it decompose the prior to independent priors, provide obvious computational convenience.] The computational convenience improved the scalability of the model.

The proposed BHAM uses a spike-and-slab prior for function selections, but it substantially differs from previous spike-and-slab based GAMs, i.e. the spike-and-slab GAM [@Scheipl2012] and the SB GAM [@Bai2021] in many ways. First of all, the proposed spike-and-slab spline prior is a spike-and-slab lasso type prior using independent mixture double exponential distribution, compared to spike-and-slab GAM. Spike-and-slab lasso priors provide computational convenience during model fitting through optimization algorithms, instead of computational intensive sampling algorithms. They make fitting high- and ultrahigh-dimensional model feasible without sacrificing performance in prediction and variable selection. Secondly, the optimization algorithms introduced in this article include EM-Coordinate Descent algorithm and EM-Iterative weighted least square algorithm for different utilities. The applications of the two aforementioned algorithm are fruitful in Bayesian hierarchical models in high-dimensional data analysis, see [TODO: add citations]. Even though SB-GAM with a group spike-and-slab lasso prior also uses EM-CD for model fitting, the proposed EM-IWLS provides uncertainty measures that could be further used for confidence bound calculation and hypothesis testing. EM-IWLS complements the lack of inference potential from EM-CD in a median and high data setting. Furthermore, the proposed model addresses the incapability of bilevel selection in SB-GAM. Lastly, the R implementation of the Bayesian hierarchical additive model is available publicly via BHAM at [https://github.com/boyiguo1/BHAM](https://github.com/boyiguo1/BHAM), make transnational science more accessible.

>>>>

To address these challenges, we propose a novel Bayesian hierarchical generalized additive model (BHAM) for high dimensional data analysis. Specifically, we impose a new bi-part spike-and-slab spline prior on the smooth functions to perform bilevel selection, where the linear and nonlinear spaces of smooth functions can be selected separately. The prior setup encourages a flexible solution, rending one of three possibilities: no effect, only linear effect, or nonlinear effect of a predictor. Additionally, two fast computing optimization-based algorithms are developed for high and ultra-high dimension settings respectively. Meanwhile, to avoid the over-penalization of the basis function coefficients, smoothness penalties are incorporated in the model via re-parameterization. Smoothness penalties are commonly implemented in GAMs through smoothing and penalized regression splines. They are quadratic norms of the coefficients and allow locally adaptive penalties on each smoothing function. For the most common cases of cubic splines, the smoothness penalty conditioning on a smoothness penalty parameter $\lambda_j$ is a function of the integration of the second derivative of the spline function, expressed mathematically as
\begin{equation}\label{eq:smoothpen}
  \text{pen}\left[f_j(x)\right] = \lambda_j \int f^{"}_j(x)dx = \lambda_j \bs \beta_j^T \bs S_j \bs \beta_j ,
\end{equation}
where $\bs S_j$ is a known smoothness penalty matrix, and $\bs \beta_j$ is the basis function coefficients. Smoothness penalties are also previously used in the spike-and-slab GAM [@Scheipl2012] and the sparsity-smoothness penalty [@Meier2009]. Moreover, incorporating the smoothness penalty allows the separation of the linear space of the smooth function, also know as the null space, from the nonlinear space. @Marra2011 introduced a re-parameterization of the basis function matrix based on the decomposition of the smoothness penalty matrix $\bs S$. The re-parameterization allows different penalties imposed on the null and nonlinear spaces separately, and further allows the sparsity in linear space and smoothness in nonlinear effect interpolation. ^[TODO: a sentence that it decompose the prior to independent priors, provide obvious computational convenience.] The computational convenience improved the scalability of the model.

The proposed BHAM uses a spike-and-slab prior for function selections, but it substantially differs from previous spike-and-slab based GAMs, i.e. the spike-and-slab GAM [@Scheipl2012] and the SB GAM [@Bai2021] in many ways. First of all, the proposed spike-and-slab spline prior is a spike-and-slab lasso type prior using independent mixture double exponential distribution, compared to spike-and-slab GAM. Spike-and-slab lasso priors provide computational convenience during model fitting through optimization algorithms, instead of computational intensive sampling algorithms. They make fitting high- and ultrahigh-dimensional models feasible without sacrificing performance in prediction and variable selection. Secondly, the optimization algorithms introduced in this article include EM-Coordinate Descent algorithm and EM-Iterative weighted least square algorithm for different utilities. The applications of the two aforementioned algorithm are fruitful in Bayesian hierarchical models in high-dimensional data analysis, see ^[TODO: add citations]. Even though SB-GAM with a group spike-and-slab lasso prior also uses EM-CD for model fitting, the proposed EM-IWLS provides uncertainty measures that could be further used for confidence bound calculation and hypothesis testing. EM-IWLS complements the lack of inference potential from EM-CD in a median and high data setting. Furthermore, the proposed model addresses the incapability of bilevel selection in SB-GAM. Lastly, the R implementation of the Bayesian hierarchical additive model is available publicly via BHAM at [https://github.com/boyiguo1/BHAM](https://github.com/boyiguo1/BHAM), make transnational science more accessible.

### 2021-06-29 Manuscript/02-Method.Rmd
* Revise the notation section of the Method * Correct typo and grammar in intro

To encourage proper smoothness of the smoothing functions, we adopt the idea of the smoothing penalty from smoothing spline models. The basic idea is to set up a smoothing penalty, depending on the smoothness penalty matrix via Equation \ref{eq:smoothpen}, in the posterior density function, or least squared and likelihood function in the penalized framework. However, direct integration of the smoothness penalty into the sparsity penalty is not obvious. Given that the smoothness penalty matrix is most often symmetric and positive semi-definite [^ we limit the discussion to univariate smoothing function. However, the penalty matrix could possibly contain multiple matrices, e.g. tensor product smoother.], the smoothness penalty matrix can be integrated to the design matrix $\bs X$ via re-parameterization. @Marra2011 introduced a re-parameterization of the basis function matrix $\bs X$ based on the decomposition of the smoothness penalty matrix $\bs S$.

 Column-wise centering and re-parameterization introduced in the GAM as random effect section[^5] are performed. The re-parameterization has two purposes. First of all the re-parameterization reshapes the columns to be linearly independent to each other, and hence, independent prior can be set to the coefficients. Secondly, the re-parameterization decomposes the model matrix $\bs X_j$ for the $j$th covariates to two sub-matrices representing the null space of the spline and penalized space of the spline,
$$
\bs X_j = \begin{bmatrix}
\bs X_j^{0} & \bs X_j^{pen}
\end{bmatrix},
$$
where $\bs X_j^{null}$ is the column space representing the null space of the spline model, and $\bs X_j^{pen}$ denotes the column spaces that need to be shrunk for smoothness of the spline. The purpose for this re-parameterization is to isolate the null space from the smoothing space, such that answering the question, if non-linear relationship is necessary, becomes easy by deciding if the corresponding coefficients of the $\bs X_j^{pen}$ are jointly zero. This strategy is widely used, previously mentioned in @Scheipl2012 and the references there in.^[Possibly select some to add here.] Hereafter, we denote the coefficients of the null space as $\bs \beta^{0}_j$ and the coefficients of the penalized space as $\bs \beta^{pen}_j$. The spline function for the $j$the covariate is 
$$
f_j(X) = f_j^0(X) + f_j^{pen}(X) = {\beta_j^0}^T X_j^0 + {\beta_j^{pen}}^T X_j^{pen}.
$$

>>>>

To encourage proper smoothness of the smoothing functions, we adopt the idea of smoothing penalties from smoothing spline models. The basic idea is to set up a smoothing penalty, depending on the smoothness penalty matrix via Equation \ref{eq:smoothpen}, in the posterior density function, or least squared and likelihood function in the penalized framework. However, the direct integration of smoothness penalties into sparsity penalties is not obvious. Given the smoothness penalty matrix is most often symmetric and positive semi-definite ^[ we limit the discussion to univariate smoothing function. However, the penalty matrix could possibly contain multiple matrices, e.g. tensor product smoother.], it can be integrated into the design matrix $\bs X$ via a re-parameterization. The re-parameterization follows @Marra2011, in which eigen-decomposed the penalty matrix $\bs S = \bs U \bs D \bs U^T$, where the matrix $\bs D$ is diagonal with the eigenvalues arranged in the ascending order. To note, $\bs D$ can contain $0$ elements on the diagonal, associated with the null space of the smooth function. We further write the orthonormal matrix $\bs U$, containing the eigenvectors as column, as an (row) augmentation of two sub-matrices $\bs U \equiv \begin{bmatrix}\bs U^0 : \bs U^{\text{pen}}\end{bmatrix}$, where $\bs U^{\text{pen}}$ contains the eigenvectors (as columns) for the non-zero eigenvalues, i.e. the penalized space, and $\bs U^0$ contains the eigenvectors for the null space. We multiply the basis function matrix $\bs X$ with the orthonormal matrix $\bs U$ for the new design matrix $\bs X^\ast = \bs X \bs U \equiv \begin{bmatrix} \bs X^0 : \bs X^{\text{pen}} \end{bmatrix}$. An additional scaling step is imposed on $\bs X^{\text{pen}}$ by the non-zero eigenvalues of $\bs D$ such that the new basis function matrix $\bs X^\ast$ is scale-invariant ^[ I know this work for tensor spline (see @Wood2006), but I am not sure if it can be generalized to all smoothing functions]. For notation convenience, we denote $\bs X_j \equiv \begin{bmatrix} \bs X_j^0 : \bs X_j^{\text{pen}} \end{bmatrix}$ as the after re-parameterized basis function matrix for the $j$th variable hereafter. Similarly, the spline function can be expressed in the matrix form
$$
f_j(x_j) = f_j^0(x_j) + f_j^\tp (x_j) = {\beta_j^0}^T \bs X_j^0 + {\beta_j^\tp}^T \bs X_j^\tp ,
$$

The re-parameterization sets up the foundation of the proposed model, which has three-fold benefits. First of all, as previously mentioned, the re-parameterization integrated the smoothness penalty into the design matrix, and hence the penalty can be expressed in the posterior density function implicitly in addition to the sparse penalty for variable and function selection. Secondly, the eigendecomposition of the smooth penalty isolates the linear space of a smooth function from the non-linear space, improving the feasibility of bi-level variable/function selection and estimation inference. The eigendecomposition also introduced the linearly independent column spaces of the smooth function matrix, which allows imposing independent priors on the coefficients. This reduces the computational complexity that multivariate priors induces, and greatly broadens the choices of priors and further model choices. Last but not least, the scaling step of $\bs X^\tp$ further simplifies the choice of penalty priors, from column-specific penalties to a unified penalty. This step is also necessary for the proposed spike-and-slab spline prior. Conventionally, the spike-and-slab priors require scaling of predictors ^[TODO: insert a citation.]

### 2021-06-29 Manuscript/SS_GAM.tex
* Revise the notation section of the Method * Correct typo and grammar in intro

\newcommand{\bs}[1]{\boldsymbol{#1}}

@@

To address these challenges, we propose a novel Bayesian hierarchical
generalized additive model (BHAM) for high dimensional data analysis.
Specifically, we impose a new bi-part spike-and-slab spline prior on the
smooth functions to perform bilevel selection, where the linear and
nonlinear spaces of smooth functions can be selected separately. The
prior setup encourages a flexible solution, rending one of three
possibilities: no effect, only linear effect, or nonlinear effect of a
predictor. Additionally, two fast computing optimization based
algorithms are developed for high and ultra-high dimension settings
respectively. Meanwhile, to avoid the over-penalization of the basis
function coefficients, smoothness penalties are incorporated in the
model via re-parameterization. Smoothness penalties are commonly
implemented in GAMs through smoothing and penalized regression splines.
They are quadratic norm of the coefficients, and allow locally adaptive
penalties on each smoothing function. For the most common case of cubic
splines, the smoothness penalty conditioning on a smoothness penalty
parameter \(\lambda_j\) is a function of the integration of second
derivative of the spline function, expressed mathematically as
\begin{equation}\label{eq:smoothpen}
  \text{pen}\left[f_j(x)\right] = \lambda_j \int f^{"}_j(x)dx = \lambda_j \boldsymbol{\beta}_j^T \boldsymbol{S}_j \boldsymbol{\beta}_j ,
\end{equation} where \(\boldsymbol{S}_j\) is a known penalty matrix, and
\(\boldsymbol{\beta}_j\) are the basis function coefficients. Smoothness
penalties are also previously used in the spike-and-slab GAM
\citep{Scheipl2012} and the sparsity-smoothness penalty
\citep{Meier2009}. Moreover, incorporating the smoothness penalty allows
the separation of the linear space of the smooth function, also know as
the null space, from the nonlinear space. \citet{Marra2011} introduced a
re-parameterization of the basis function matrix based on the
decomposition of the smoothness penalty matrix \(\boldsymbol{S}\). The
re-parameterization allows different penalties imposed on the null and
nonlinear spaces separately, and further allows the sparsity in linear
space and smoothness in nonlinear effect interpolation. {[}TODO: a
sentence that it decompose the prior to independent priors, provide
obvious computational convenience.{]} The computational convenience
improved the scalability of the model.

The proposed BHAM uses a spike-and-slab prior for function selections,
but it substantially differs from previous spike-and-slab based GAMs,
i.e.~the spike-and-slab GAM \citep{Scheipl2012} and the SB GAM
\citep{Bai2021} in many ways. First of all, the proposed spike-and-slab
spline prior is a spike-and-slab lasso type prior using independent
mixture double exponential distribution, compared to spike-and-slab GAM.
Spike-and-slab lasso priors provide computational convenience during
model fitting through optimization algorithms, instead of computational
intensive sampling algorithms. They make fitting high- and
ultrahigh-dimensional model feasible without sacrificing performance in
prediction and variable selection. Secondly, the optimization algorithms
introduced in this article include EM-Coordinate Descent algorithm and
EM-Iterative weighted least square algorithm for different utilities.
The applications of the two aforementioned algorithm are fruitful in
Bayesian hierarchical models in high-dimensional data analysis, see
{[}TODO: add citations{]}. Even though SB-GAM with a group
spike-and-slab lasso prior also uses EM-CD for model fitting, the
proposed EM-IWLS provides uncertainty measures that could be further
used for confidence bound calculation and hypothesis testing. EM-IWLS
complements the lack of inference potential from EM-CD in a median and
high data setting. Furthermore, the proposed model addresses the
incapability of bilevel selection in SB-GAM. Lastly, the R
implementation of the Bayesian hierarchical additive model is available
publicly via BHAM at \url{https://github.com/boyiguo1/BHAM}, make
transnational science more accessible.

@@

To encourage proper smoothness of the smoothing functions, we adopt the
idea of the smoothing penalty from smoothing spline models. The basic
idea is to set up a smoothing penalty, depending on the smoothness
penalty matrix via Equation \ref{eq:smoothpen}, in the posterior density
function, or least squared and likelihood function in the penalized
framework. However, direct integration of the smoothness penalty into
the sparsity penalty is not obvious. Given that the smoothness penalty
matrix is most often symmetric and positive semi-definite {[}\^{} we
limit the discusstion to univariate smoothing function. However, the
penalty matrix could possibly contain multiple matrices, e.g.~tensor
product smoother.{]}, the smoothness penalty matrix can be integrated to
the design matrix \(\boldsymbol{X}\) via re-parameterization.
\citet{Marra2011} introduced a re-parameterization of the basis function
matrix \(\boldsymbol{X}\) based on the decomposition of the smoothness
penalty matrix \(\boldsymbol{S}\).

Column-wise centering and re-parameterization introduced in the GAM as
random effect section{[}\^{}5{]} are performed. The re-parameterization
has two purposes. First of all the re-parameterization reshapes the
columns to be linearly independent to each other, and hence, independent
prior can be set to the coefficients. Secondly, the re-parameterization
decomposes the model matrix \(\boldsymbol{X}_j\) for the \(j\)th
covariates to two sub-matrices representing the null space of the spline
and penalized space of the spline, \[
\boldsymbol{X}_j = \begin{bmatrix}
\boldsymbol{X}_j^{0} & \boldsymbol{X}_j^{pen}
\end{bmatrix},
\] where \(\boldsymbol{X}_j^{null}\) is the column space representing
the null space of the spline model, and \(\boldsymbol{X}_j^{pen}\)
denotes the column spaces that need to be shrunk for smoothness of the
spline. The purpose for this re-parameterization is to isolate the null
space from the smoothing space, such that answering the question, if
non-linear relationship is necessary, becomes easy by deciding if the
corresponding coefficients of the \(\boldsymbol{X}_j^{pen}\) are jointly
zero. This strategy is widely used, previously mentioned in
\citet{Scheipl2012} and the references there in.\footnote{Possibly
  select some to add here.} Hereafter, we denote the coefficients of the
null space as \(\boldsymbol{\beta}^{0}_j\) and the coefficients of the
penalized space as \(\boldsymbol{\beta}^{pen}_j\). The spline function
for the \(j\)the covariate is \[
f_j(X) = f_j^0(X) + f_j^{pen}(X) = {\beta_j^0}^T X_j^0 + {\beta_j^{pen}}^T X_j^{pen}.
\]

>>>>

\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\tp}{\text{pen}}

@@

To address these challenges, we propose a novel Bayesian hierarchical
generalized additive model (BHAM) for high dimensional data analysis.
Specifically, we impose a new bi-part spike-and-slab spline prior on the
smooth functions to perform bilevel selection, where the linear and
nonlinear spaces of smooth functions can be selected separately. The
prior setup encourages a flexible solution, rending one of three
possibilities: no effect, only linear effect, or nonlinear effect of a
predictor. Additionally, two fast computing optimization-based
algorithms are developed for high and ultra-high dimension settings
respectively. Meanwhile, to avoid the over-penalization of the basis
function coefficients, smoothness penalties are incorporated in the
model via re-parameterization. Smoothness penalties are commonly
implemented in GAMs through smoothing and penalized regression splines.
They are quadratic norms of the coefficients and allow locally adaptive
penalties on each smoothing function. For the most common cases of cubic
splines, the smoothness penalty conditioning on a smoothness penalty
parameter \(\lambda_j\) is a function of the integration of the second
derivative of the spline function, expressed mathematically as
\begin{equation}\label{eq:smoothpen}
  \text{pen}\left[f_j(x)\right] = \lambda_j \int f^{"}_j(x)dx = \lambda_j \boldsymbol{\beta}_j^T \boldsymbol{S}_j \boldsymbol{\beta}_j ,
\end{equation} where \(\boldsymbol{S}_j\) is a known smoothness penalty
matrix, and \(\boldsymbol{\beta}_j\) is the basis function coefficients.
Smoothness penalties are also previously used in the spike-and-slab GAM
\citep{Scheipl2012} and the sparsity-smoothness penalty
\citep{Meier2009}. Moreover, incorporating the smoothness penalty allows
the separation of the linear space of the smooth function, also know as
the null space, from the nonlinear space. \citet{Marra2011} introduced a
re-parameterization of the basis function matrix based on the
decomposition of the smoothness penalty matrix \(\boldsymbol{S}\). The
re-parameterization allows different penalties imposed on the null and
nonlinear spaces separately, and further allows the sparsity in linear
space and smoothness in nonlinear effect interpolation. \footnote{TODO:
  a sentence that it decompose the prior to independent priors, provide
  obvious computational convenience.} The computational convenience
improved the scalability of the model.

The proposed BHAM uses a spike-and-slab prior for function selections,
but it substantially differs from previous spike-and-slab based GAMs,
i.e.~the spike-and-slab GAM \citep{Scheipl2012} and the SB GAM
\citep{Bai2021} in many ways. First of all, the proposed spike-and-slab
spline prior is a spike-and-slab lasso type prior using independent
mixture double exponential distribution, compared to spike-and-slab GAM.
Spike-and-slab lasso priors provide computational convenience during
model fitting through optimization algorithms, instead of computational
intensive sampling algorithms. They make fitting high- and
ultrahigh-dimensional models feasible without sacrificing performance in
prediction and variable selection. Secondly, the optimization algorithms
introduced in this article include EM-Coordinate Descent algorithm and
EM-Iterative weighted least square algorithm for different utilities.
The applications of the two aforementioned algorithm are fruitful in
Bayesian hierarchical models in high-dimensional data analysis, see
\footnote{TODO: add citations}. Even though SB-GAM with a group
spike-and-slab lasso prior also uses EM-CD for model fitting, the
proposed EM-IWLS provides uncertainty measures that could be further
used for confidence bound calculation and hypothesis testing. EM-IWLS
complements the lack of inference potential from EM-CD in a median and
high data setting. Furthermore, the proposed model addresses the
incapability of bilevel selection in SB-GAM. Lastly, the R
implementation of the Bayesian hierarchical additive model is available
publicly via BHAM at \url{https://github.com/boyiguo1/BHAM}, make
transnational science more accessible.

@@

To encourage proper smoothness of the smoothing functions, we adopt the
idea of smoothing penalties from smoothing spline models. The basic idea
is to set up a smoothing penalty, depending on the smoothness penalty
matrix via Equation \ref{eq:smoothpen}, in the posterior density
function, or least squared and likelihood function in the penalized
framework. However, the direct integration of smoothness penalties into
sparsity penalties is not obvious. Given the smoothness penalty matrix
is most often symmetric and positive semi-definite \footnote{ we limit
  the discussion to univariate smoothing function. However, the penalty
  matrix could possibly contain multiple matrices, e.g.~tensor product
  smoother.}, it can be integrated into the design matrix
\(\boldsymbol{X}\) via a re-parameterization. The re-parameterization
follows \citet{Marra2011}, in which eigen-decomposed the penalty matrix
\(\boldsymbol{S} = \boldsymbol{U} \boldsymbol{D} \boldsymbol{U}^T\),
where the matrix \(\boldsymbol{D}\) is diagonal with the eigenvalues
arranged in the ascending order. To note, \(\boldsymbol{D}\) can contain
\(0\) elements on the diagonal, associated with the null space of the
smooth function. We further write the orthonormal matrix
\(\boldsymbol{U}\), containing the eigenvectors as column, as an (row)
augmentation of two sub-matrices
\(\boldsymbol{U} \equiv \begin{bmatrix}\boldsymbol{U}^0 : \boldsymbol{U}^{\text{pen}}\end{bmatrix}\),
where \(\boldsymbol{U}^{\text{pen}}\) contains the eigenvectors (as
columns) for the non-zero eigenvalues, i.e.~the penalized space, and
\(\boldsymbol{U}^0\) contains the eigenvectors for the null space. We
multiply the basis function matrix \(\boldsymbol{X}\) with the
orthonormal matrix \(\boldsymbol{U}\) for the new design matrix
\(\boldsymbol{X}^\ast = \boldsymbol{X} \boldsymbol{U} \equiv \begin{bmatrix} \boldsymbol{X}^0 : \boldsymbol{X}^{\text{pen}} \end{bmatrix}\).
An additional scaling step is imposed on \(\boldsymbol{X}^{\text{pen}}\)
by the non-zero eigenvalues of \(\boldsymbol{D}\) such that the new
basis function matrix \(\boldsymbol{X}^\ast\) is scale-invariant
\footnote{ I know this work for tensor spline (see \citet{Wood2006}),
  but I am not sure if it can be generalized to all smoothing functions}.
For notation convenience, we denote
\(\boldsymbol{X}_j \equiv \begin{bmatrix} \boldsymbol{X}_j^0 : \boldsymbol{X}_j^{\text{pen}} \end{bmatrix}\)
as the after re-parameterized basis function matrix for the \(j\)th
variable hereafter. Similarly, the spline function can be expressed in
the matrix form \[
f_j(x_j) = f_j^0(x_j) + f_j^\text{pen}(x_j) = {\beta_j^0}^T \boldsymbol{X}_j^0 + {\beta_j^\text{pen}}^T \boldsymbol{X}_j^\text{pen},
\]

The re-parameterization sets up the foundation of the proposed model,
which has three-fold benefits. First of all, as previously mentioned,
the re-parameterization integrated the smoothness penalty into the
design matrix, and hence the penalty can be expressed in the posterior
density function implicitly in addition to the sparse penalty for
variable and function selection. Secondly, the eigendecomposition of the
smooth penalty isolates the linear space of a smooth function from the
non-linear space, improving the feasibility of bi-level
variable/function selection and estimation inference. The
eigendecomposition also introduced the linearly independent column
spaces of the smooth function matrix, which allows imposing independent
priors on the coefficients. This reduces the computational complexity
that multivariate priors induces, and greatly broadens the choices of
priors and further model choices. Last but not least, the scaling step
of \(\boldsymbol{X}^\text{pen}\) further simplifies the choice of
penalty priors, from column-specific penalties to a unified penalty.
This step is also necessary for the proposed spike-and-slab spline
prior. Conventionally, the spike-and-slab priors require scaling of
predictors \footnote{TODO: insert a citation.}
